### 2023-07-11 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes

\textcolor{red}{Back of the envelope calculation shows that anything
with reduced area greater than 0.8 can not pass through the stenosis,
assuming the vesicle shape is an ellipse}
We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
multicomponent vesicle with an initially random distribution of lipids.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. We first consider the three different
energies---bending, tension, and phase---for each of the
single-component and multicomponent vesicles. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center of mass. As a reminder, the vesicle enters the
constriction at $x=-15$ and exits at $x=15$. Also note that the
single-component vesicle does not have a phase energy. A few general
trends can immediately be seen. First, as the vesicle enters the
stenosis, there are sharp jumps in both the tension and bending
energies, as expected. Next, the multicomponent vesicles only coarsen
when the vesicle is not in the stenosis. Finally, when coarsening does
occur, there are rapid changes in the tension energy.

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
  \todo[inline]{need to redo these plots}
\end{figure}

@@

%\begin{comment}
%\begin{figure}[h]
\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
  with bending modulus $b=1$; (b) single-component with bending modulus
  $b=0.55$; (c) multicomponent.}
%  The multicomponent vesicle travels
%  slightly faster, so it leaves the stenosed region earlier than the
%  single-component cases (see Figure~\ref{fig:vesVelocity}).}
%\end{figure}
\end{figure*}
%\end{comment}

>>>>

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. The initial lipid distribution of the multicomponent is random.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize any tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region.
However, in general, there is little difference between these cases,
partially because these vesicles have a large reduced area. With the
current setup, an elliptical vesicle with reduced area greater than
$\alpha = 0.8$ cannot fit through the closely-fitting geometry.

\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig6a.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig6b.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig6c.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) single-component
  with bending modulus $b=1$; (b) single-component with bending modulus
  $b=0.55$; (c) multicomponent.}
\end{figure*}

To create more significant differences between the three cases, we
consider the same geometry, but for a vesicle with reduced area $\alpha
= 0.4$. Figure~\ref{fig:RA4} shows six time steps of a (a) stiff
single-component, (b) floppy single-component, and (c) multicomponent
vesicle. We first consider the three different energies---bending,
tension, and phase---for each of these cases.  In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. A few general trends can
immediately be seen. First, as the vesicle enters the stenosis, there
are sharp jumps in both the tension and bending energies, as expected.
Next, the multicomponent vesicles only coarsen when the vesicle is not
in the stenosis. Finally, when coarsening does occur, there are rapid
changes in the tension energy.

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
  \todo[inline]{need to redo these plots}
\end{figure}

@@
